---
title: "Alcohol vs Seat choice"
author: "Laizha Grajeda De Leon"
date: "Summer 2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
require(tidyverse)
require(tigerstats)
davisdata <- read.csv(file="UCDavis.csv")
```
## Our Goal is to answer this question Is there a difference between the alcohol consumed between the row
## you choose to sit in??

## Now with ggplot - first select the basic data

```{r}
basicCN <- ggplot(davisdata,aes(y=alcohol,x=Seat))
```
## Now add in boxplot



```{r}
basicCN + geom_boxplot()
```
  
  
### get fancy  

```{r}
basicCN + geom_boxplot(notch=TRUE,outlier.color = "red") + stat_boxplot(geom ='errorbar') + labs(title="Fancy notch boxplot \n with 2 lines")
```

The median and first/third percentiles for the "back" seat box plot are significantly higher as compared to the "front" and "middle" seats, including the max. The "front" seat data seemed to have the lowest median and maximum, while the "middle" data had the most outliers. The people in the "back" seats seemed to consume more alcohol compared to the pople in the "front" and "middle".


## Numerical Summarys 

```{r}
favstats(alcohol~Seat,data=davisdata)
```

Though the middle row had the most people (n=83), the "back" row had the highest median, max, Q1/Q3, and mean, suggesting that those in the back had higher levels of alcohol consumption. 

## Inferential Tests

## Conclusions


