---
title: "Alcohol vs Seat choice"
author: "Laizha Grajeda De Leon"
date: "Summer 2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
require(tidyverse)
require(tigerstats)
davisdata <- read.csv(file="UCDavis.csv")
```
## Our Goal is to answer this question Is there a difference between the alcohol consumed between the row
## you choose to sit in??

## Now with ggplot - first select the basic data

```{r}
basicCN <- ggplot(davisdata,aes(y=alcohol,x=Seat))
```
## Now add in boxplot



```{r}
basicCN + geom_boxplot()
```
  
  
### get fancy  

```{r}
basicCN + geom_boxplot(notch=TRUE,outlier.color = "red") + stat_boxplot(geom ='errorbar') + labs(title="Fancy notch boxplot \n with 2 lines")
```

The median and first/third percentiles for the "back" seat box plot are significantly higher as compared to the "front" and "middle" seats, including the max. The "front" seat data seemed to have the lowest median and maximum, while the "middle" data had the most outliers. The people in the "back" seats seemed to consume more alcohol compared to the people in the "front" and "middle".


## Numerical Summarys 

```{r}
favstats(alcohol~Seat,data=davisdata)
```

Though the middle row had the most people (n=83), the "back" row had the highest median, max, Q1/Q3, and mean, suggesting that those in the back had higher levels of alcohol consumption. 

## Inferential Tests

```{r}
model1 <- aov(alcohol~Seat,data=davisdata)
summary.aov(model1)
```

Low p-level indicates issue in data, and warrants further statistical testing through a TurkeyHSD test. 

```{r}
plot(TukeyHSD(model1))
```

The front-back difference consistently yields a negative number, indicating that there is an actual difference between the alcohol consumption of the front rows and that of the middle rows; this observation also persists for the middle-back data. The differences between the middle and the front rows aren't as large compared to the other two categories, even passing zero at an instance, showing that the middle and the front rows are not that differnt from one another. 

## Conclusions


